---
title: "POI Services Analysis & Mapping"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

require(tidyverse)
require(sf)
#library(arcgisbinding)
library(tmap)
library(kableExtra)
library(rpgcolorsr)

epsg <- 2236

tmap_mode("view")

#arc.check_product()

options(scipen=999)

grid_with_summary <- readRDS("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/data_prep/demo_data/services_count_overlay/services_count_grid.rds")

merged_points <- readRDS("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/data_prep/demo_data/services_count_overlay/services_merged_points.rds")
```

## Summary

The purpose of this page is to review the method and process for acquiring and summarizing service-oriented POIs in the D4 region.

## Input Data

The following POIs were queried from Open Street Map:

-   Town Hall
-   Post Office
-   Police
-   Fire Station
-   Courthouse
-   Library
-   Government

## Analysis

500-foot grid cells were created. The number of unique POI categories within 1,000 feet from the center of each cell was calculated, returning a value of 0-7 for each cell, with 7 representing all POI types are present, and 0 representing no POIs present.

### Map of Results

*Note: you may need to zoom in to see grid cells.*

```{r}


tm_shape(grid_with_summary) + tm_fill(col = "count", palette = "-inferno") +
  tm_shape(merged_points) + tm_dots(col = "type", 
                                  border.lwd = 0,
                                  palette = "viridis")

```
