---
title: "POI Services Analysis & Mapping"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

```{r, include = FALSE, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

require(tidyverse)
require(sf)
#library(arcgisbinding)
library(tmap)
library(kableExtra)
library(rpgcolorsr)
library(tmaptools)
library(rmapshaper)

epsg <- 2236

tmap_mode("view")

#arc.check_product()

options(scipen=999)

grid_with_summary <- readRDS("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/data_prep/demo_data/services_count_overlay/services_count_grid.rds")

merged_points <- readRDS("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/data_prep/demo_data/services_count_overlay/services_merged_points.rds")
```

## Summary

The purpose of this page is to review the method and process for acquiring and summarizing service-oriented POIs in the D4 region.

## Input Data

The following POIs were queried from Open Street Map:

-   Town Hall
-   Post Office
-   Police
-   Fire Station
-   Courthouse
-   Library
-   Government

## Analysis

500-foot grid cells were created. The number of unique POI categories within 1,000 feet from the center of each cell was calculated, returning a value of 0-7 for each cell, with 7 representing all POI category types are present, and 0 representing no POI category types are present.

### Summary of Results

#### Map (Locations with score with score of 3 or higher)

```{r}

three_plus_points <- grid_with_summary %>% 
  filter(count > 2) %>%
  ms_dissolve() %>% 
  ms_explode() %>% 
  st_centroid() %>% 
  rename(geometry = x)

three_plus_gird <- grid_with_summary %>% 
  filter(count > 2)

geocoded_points <- rev_geocode_OSM(three_plus_points, projection = 2236)

geocoded_points <- geocoded_points %>%
  mutate(display_name = if_else(is.na(town),
                                if_else(is.na(suburb), village, suburb),town),
         display_name = if_else(is.na(display_name), city, display_name),
         display_name = if_else(is.na(display_name),
           case_when(office == "City of Coral Springs City Hall" ~ "Coral Springs"), display_name))
           

points_with_geocode <- cbind(three_plus_points, geocoded_points)

tm_shape(three_plus_gird) + tm_polygons(col = "count", 
                                  border.lwd = 0,
                                  palette = "viridis", alpha = 0.5) +
  tm_shape(points_with_geocode) + tm_dots(col = "#F29C20", size = 0.1,
                                          perceptual = TRUE) +
  tm_text("display_name", remove.overlap = TRUE, just = "bottom") +
  tm_add_legend(type = "fill", label = "Place w/ 3+ Categories", col = "#F29C20", )
```

#### Table of Places With 3+ POI Categories Within 1,000 Feet

```{r}

points_with_geocode %>%
  st_drop_geometry() %>%
  distinct(county, display_name) %>% 
  kbl(col.names = c("County", "Place Name")) %>% 
  kable_paper("hover", full_width = F)

```

#### Map of all POIs + summarized grid cells

*Note: you may need to zoom in to see grid cells.*

```{r}


tm_shape(grid_with_summary) + tm_fill(col = "count", palette = "-inferno") +
  tm_shape(merged_points) + tm_dots(col = "type", border.lwd = 0,
                                  palette = "viridis")

```
