---
title: "Relationship Between SPCC 1.0 & FEMA National Flood Hazard Layer"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r, include = FALSE, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(sf)
library(tmap)
library(kableExtra)
library(readr)
library(ggplot2)
library(plotly)
library(rpgcolorsr)
library(stringr)
library(rmapshaper)

options(width = 2000)

tmap_mode("view")

options(scipen=999)

epsg <- 2236
```

## Analysis Overview

This analysis quantifies relationships between SPCC 1.0 Refined Smoothed
Roadway Segments and flood hazard areas identified in FEMA's Flood
Insurance Rate Map (FIRM). For this analysis, FIRM GIS data for the
state of Florida were obtained from the [FGDL data
repository](https://www.fgdl.org/metadataexplorer/explorer.jsp) in March
2021. This analysis identified the floodplain of each roadway segment
using the roadway centerline's relationship to FIRM polygons.

```{r}

study_area <- st_read("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/data_prep/cleaned_data/study_area/study_area.shp", quiet = T) %>% 
  st_transform(epsg)

flood_hazard <- st_read("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/equity_resiliency/dfirm_fldhaz_oct20_clip.shp", quiet = T) %>% 
  st_transform(epsg)

flood_hazard_simp <- flood_hazard %>% 
  ms_simplify()

spcc10 <- st_read("K:/Projects/D4_CSHnetwork/Features/LU/SPCC/SPCC_V1_0_Final_w_metadata/Outputs/Districtwide_Refined_ver_1_0.gdb", layer = "Existing_RefinedSmoothedSegs_ver_1_0", quiet = T) %>% 
  st_transform(epsg) %>% 
  st_zm()

spcc_flood_intersect <- st_read("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/equity_resiliency/spcc_10_flood_intersect.shp", quiet = T) %>% 
  st_transform(epsg) %>% 
  st_zm() %>% 
  select(GCODE_DESC, FLOODPLAIN, ROADID)

```

## Mapping

### SPCC 1.0 Segments by Floodplain Designation

The following map presents all roadway segments in the SPCC 1.0 Refined
Smoothed dataset, symbolized based on the FEMA floodplain classification
zone that it resides within. In cases where a roadway segment crossed
more than one zone, the roadway segment was split.

```{r}

MyPal <- rpg_color_pal("rpg_rainbow_no_grey")(5)

spcc_flood_intersect_simp <- ms_simplify(spcc_flood_intersect)

tm_shape(spcc_flood_intersect_simp) + tm_lines(col = "FLOODPLAIN", 
                                          palette = MyPal, lwd = 2, title.col = "SPCC Segments by Floodplain")

```

## Tables and Charts

### Floodplain Designations by SPCC 1.0 Refined Smoothed Classification

The following table and charts present the presence of the five FEMA
floodplain classifications for each SPCC 1.0 Refined Smoothed
classification.

```{r}

spcc_intersect <- spcc_flood_intersect %>%
  select(GCODE_DESC, FLOODPLAIN) %>% 
  mutate(linear_feet = as.numeric(st_length(.))) %>%
  filter(linear_feet > 0) %>% 
  st_drop_geometry() %>% 
  group_by(GCODE_DESC, FLOODPLAIN) %>%
  summarise(linear_feet = sum(linear_feet)) 

spcc_intersect %>% 
  pivot_wider(names_from = FLOODPLAIN, values_from = linear_feet) %>% 
  kbl(col.names = c("SPCC 1.0", "100-Year Floodplain", "500-Year Floodplain", 
                    "Open Water", "Outside Floodplain", "Undetermined"),
     format.args = list(digits = 0, big.mark = ",")) %>% 
  kable_paper("hover", full_width = F) %>% 
  add_header_above(c("SPCC 1.0", "FEMA Floodplain Designation" = 5))

```

```{r}

# Small multiple
ggplotly(ggplot(spcc_intersect, aes(fill=FLOODPLAIN, y=linear_feet, x=GCODE_DESC)) + 
    geom_bar(position="fill", stat="identity") +
    scale_fill_rpg(palette = "rpg_colors") +
    ggtitle("SPCC by FEMA Flood Classification - Percent") +
    xlab("") +
    ylab("% of Roadway") +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)))

```

```{r}
# Small multiple
ggplotly(ggplot(spcc_intersect, aes(fill=FLOODPLAIN, y=linear_feet, x=GCODE_DESC)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_rpg(palette = "rpg_colors") +
    ggtitle("SPCC by FEMA Flood Classification - Linear Feet") +
    xlab("") +
    ylab("Linear Feet of Roadway") +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)))

```
