---
title: "Relationship Between SPCC 1.0 & Zero Vehicle Households"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r, include = FALSE, echo = FALSE}

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(sf)
library(tmap)
library(kableExtra)
library(readr)
library(ggplot2)
library(plotly)
library(rpgcolorsr)
library(stringr)
library(rmapshaper)
library(classInt)

options(width = 2000)

tmap_mode("view")

options(scipen=999)

epsg <- 2236
```

## Analysis Overview

This analysis quantifies relationships between SPCC 1.0 Refined Smoothed
Roadway Segments and households with no access to vesicles as identified
in the 2018 American Community Survey.

```{r}

study_area <- st_read("K:/Projects/D4_CSHnetwork/Features/LU/SPCC_20/data_prep/cleaned_data/study_area/study_area.shp", quiet = T) %>% 
  st_transform(epsg)

spcc10 <- st_read("K:/Projects/D4_CSHnetwork/Features/LU/SPCC/SPCC_V1_0_Final_w_metadata/Outputs/Districtwide_Refined_ver_1_0.gdb", layer = "Existing_RefinedSmoothedSegs_ver_1_0", quiet = T) %>% 
  st_transform(epsg) %>% 
  st_zm()

zero_veh_hh <- st_read('K:/Projects/FLdemographic/cenacs_2018/cenacs_2018.shp', quiet = T) %>%   st_transform(epsg) %>% 
  mutate(acres = as.numeric(st_area(.))/43560,
         veh_0_per_acre = VEHICLE_0 / acres) %>% 
  select(veh_0_per_acre)

breaks_density <- classIntervals(zero_veh_hh$veh_0_per_acre, n=4, style='quantile')

zero_veh_hh$density_cat <- cut(zero_veh_hh$veh_0_per_acre, breaks = breaks_density$brks)

spcc10_0veh_density_intersect <- st_intersection(spcc10, zero_veh_hh)


```

## Mapping 

### SPCC 1.0 Segments by Density of Zero Vehicle Households

The following map presents all roadway segments in the SPCC 1.0 Refined
Smoothed dataset, symbolized based on the density of zero vehicle
households in the Census block group the roadway traverses. Zero vehicle
household density is divided into four quantiles across the entire D4
study area.

```{r}

MyPal <- rpg_color_pal("logo")(4)


tm_shape(spcc10_0veh_density_intersect) + tm_lines(col = "density_cat", 
                                          palette = MyPal, lwd = 2, 
                                          title.col = "SPCC Segments by 0 Vehicle HH Density")

```

## Tables and Charts

### Zero Vehicle Households Quantiles by SPCC 1.0 Refined Smoothed Classification

The following table and charts present the absolute and relative
presence of each of the five zero vehicle household quantile
classifications for each SPCC 1.0 Refined Smoothed classification.

```{r}

spcc_intersect <- spcc10_0veh_density_intersect %>%
  select(GCODE_DESC, density_cat) %>% 
  mutate(linear_feet = as.numeric(st_length(.)),
         density_cat = replace_na(as.character(density_cat), "No 0-Vehicle Data")) %>%
  filter(linear_feet > 0) %>% 
  st_drop_geometry() %>%
  group_by(GCODE_DESC, density_cat) %>%
  summarise(linear_feet = sum(linear_feet)) 

spcc_intersect %>% 
  pivot_wider(names_from = density_cat, values_from = linear_feet) %>% 
  kbl(col.names = c("SPCC 1.0", "Quant. 1 (low density)", "Quant. 2 (med. low)", 
                    "Quant. 3 (med. high)", "Quant. 4 (high)", "No 0-Vehicle Data"),
     format.args = list(digits = 0, big.mark = ",")) %>% 
  kable_paper("hover", full_width = F) %>% 
  add_header_above(c("SPCC 1.0", "0-Vehicle Household Density Quantile" = 5))

```

```{r}

# Small multiple
ggplotly(ggplot(spcc_intersect, aes(fill=density_cat, y=linear_feet, x=GCODE_DESC)) + 
    geom_bar(position="fill", stat="identity") +
    scale_fill_rpg(palette = "rpg_colors") +
    ggtitle("SPCC by 0 Vehicle Household Density Quantile (Proportional)") +
    xlab("") +
    ylab("% of Roadway") +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
    labs(fill = "Quantile (0-veh. HH / Ac)"))

```

```{r}
# Small multiple
ggplotly(ggplot(spcc_intersect, aes(fill=density_cat, y=linear_feet, x=GCODE_DESC)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_rpg(palette = "rpg_colors") +
    ggtitle("SPCC by 0 Vehicle Household Density Quantile (Absolute)") +
    xlab("") +
    ylab("Linear Feet of 0-Vehicle HH Quantile Classification") +
    scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
    labs(fill = "Quantile (0-veh. HH / Ac)"))

```
